Supplementary Materials for Differences in the Risk of Grade Retention for Biracial and Monoracial Students in the US, 2010-2019

### 2023-03-13 products/paper/supp_materials.qmd
Add table in supplementary materials to address issue #33

```{r}
#| label: setup
#| include: false
library(here)
source(here("analysis","check_packages.R"))
source(here("analysis","useful_functions.R"))
load(here("analysis","output","bic_spec_tests.RData"))
load(here("analysis","output","model_summaries.RData"))
load(here("analysis","output","acs.RData"))
```

@@

```{r}
#| label: create-design
acs_design <- acs %>%
  as_survey_design(ids = cluster, weights = perwt)
```

@@

```{r desc-stats-ses}
#| label: tbl-desc-stats-ses
#| tbl-cap: Socioeconomic resources by race. Shading indicates biracial group. All results apply survey weights.

tbl_summary <- acs_design %>%
  group_by(race) %>%
  summarize(fam_inc=survey_mean(family_income, vartype = NULL))

@@

```{r}
#| label: tbl-desc-stats-cult
#| tbl-cap: Cultural resources by race. Shading indicates biracial group. All results apply survey weights.
tbl_summary <- acs_design %>%
  group_by(race) %>%
  summarize(f_born=round(survey_mean(foreign_born, vartype = NULL), 3)*100,
            father_fb=round(survey_mean(foreign_born_father, 
                                        vartype = NULL), 3)*100,
            mother_fb=round(survey_mean(foreign_born_mother, 
                                        vartype = NULL), 3)*100,
            spk_eng_no=round(survey_mean(spk_eng=="No", vartype = NULL), 3)*100,
            spk_eng_some=round(survey_mean(spk_eng=="Somewhat", 
                                           vartype = NULL), 3)*100,
            spk_eng_yes=round(survey_mean(spk_eng=="Yes", vartype = NULL), 3)*100,
            f_spk_eng_no=round(survey_mean(spk_eng_father=="No", 
                                           vartype = NULL), 3)*100,
            f_spk_eng_some=round(survey_mean(spk_eng_father=="Somewhat", 
                                             vartype = NULL), 3)*100,
            f_spk_eng_yes=round(survey_mean(spk_eng_father=="Yes", 
                                            vartype = NULL), 3)*100,
            m_spk_eng_no=round(survey_mean(spk_eng_mother=="No", 
                                           vartype = NULL), 3)*100,
            m_spk_eng_some=round(survey_mean(spk_eng_mother=="Somewhat", 
                                             vartype = NULL), 3)*100,
            m_spk_eng_yes=round(survey_mean(spk_eng_mother=="Yes", 
                                            vartype = NULL), 3)*100)

>>>>

```{r}
#| label: setup
#| include: false
library(here)
source(here("analysis","check_packages.R"))
source(here("analysis","useful_functions.R"))
load(here("analysis","output","bic_spec_tests.RData"))
load(here("analysis","output","model_summaries.RData"))
load(here("analysis","output","marg_prob_alt.RData"))
load(here("analysis","output","acs.RData"))
```

@@

```{r}
#| label: create-design
#| eval: false
acs_design <- acs %>%
  as_survey_design(ids = cluster, weights = perwt)
```

@@

```{r marg-fit-table}
#| label: tbl-marg-fit
#| tbl-cap: Marginal probabilities of grade retention by racial group across models using different specifications to model the the temporal trend in grade retention by current grade of the student.
marg_prob_alt %>%
  mutate(baseline=percent(round(baseline, 5)),
         year_dummy=percent(round(year_dummy, 5)),
         year_linear=percent(round(year_linear, 5)),
         year_dummy_interact=percent(round(year_dummy_interact, 5)),
         year_linear_interact=percent(round(year_linear_interact, 5)),
         year_grade_state=percent(round(year_grade_state, 5))) %>%
  kbl(booktabs=TRUE, linesep=NULL,
      align = c("l",rep("r", ncol(marg_prob_alt)-1)),
      col.names=c("Race", "No Covariates", "Year as dummy", 
                  "Year as linear", "Year (dummy) x Grade",
                  "Year (linear) x Grade", 
                  "Year (linear) x Grade and State")) %>%
  add_header_above(c(" " = 2, 
                     "Sensitivity tests on calendar year x grade coding" = 5)) %>%
  column_spec(2:7, width = "1.75cm") %>%
  footnote(general = "All models except no covariate case include dummies for current grade and state")
```

```{r desc-stats-ses}
#| label: tbl-desc-stats-ses
#| tbl-cap: Socioeconomic resources by race. Shading indicates biracial group. All results apply survey weights.
#| eval: false
tbl_summary <- acs_design %>%
  group_by(race) %>%
  summarize(fam_inc=survey_mean(family_income, vartype = NULL))

@@

```{r}
#| label: tbl-desc-stats-cult
#| tbl-cap: Cultural resources by race. Shading indicates biracial group. All results apply survey weights.
#| eval: false
tbl_summary <- acs_design %>%
  group_by(race) %>%
  summarize(f_born=round(survey_mean(foreign_born, vartype = NULL), 3)*100,
            father_fb=round(survey_mean(foreign_born_father, 
                                        vartype = NULL), 3)*100,
            mother_fb=round(survey_mean(foreign_born_mother, 
                                        vartype = NULL), 3)*100,
            spk_eng_no=round(survey_mean(spk_eng=="No", vartype = NULL), 3)*100,
            spk_eng_some=round(survey_mean(spk_eng=="Somewhat", 
                                           vartype = NULL), 3)*100,
            spk_eng_yes=round(survey_mean(spk_eng=="Yes", vartype = NULL), 3)*100,
            f_spk_eng_no=round(survey_mean(spk_eng_father=="No", 
                                           vartype = NULL), 3)*100,
            f_spk_eng_some=round(survey_mean(spk_eng_father=="Somewhat", 
                                             vartype = NULL), 3)*100,
            f_spk_eng_yes=round(survey_mean(spk_eng_father=="Yes", 
                                            vartype = NULL), 3)*100,
            m_spk_eng_no=round(survey_mean(spk_eng_mother=="No", 
                                           vartype = NULL), 3)*100,
            m_spk_eng_some=round(survey_mean(spk_eng_mother=="Somewhat", 
                                             vartype = NULL), 3)*100,
            m_spk_eng_yes=round(survey_mean(spk_eng_mother=="Yes", 
                                            vartype = NULL), 3)*100)
